%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeExp
{Amazon Web Services (AWS)}{Cloud Consultant – Professional Services (DevOps/MLOps)}{Aug 2024 – Present}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] \textbf{Lead DevOps Consultant – RWS (Feb 2026 – Present):} Designed and shipped the multi-account cloud platform onboarding 50+ application workloads into 135+ AWS accounts; authored the Terraform + GitHub Actions provisioning pipeline that reduced per-account infrastructure setup from 3+ days to under 4 hours (\textasciitilde90\% cut). Built Transit Gateway hub-and-spoke networking with VPN/Direct Connect hybrid connectivity and centralized egress inspection, and codified preventative SCPs, tag policies, AWS Config rules, and Security Hub standards aligned to CCMv4.
    \item[$\diamond$] \textbf{DevOps Consultant – State Street (Oct 2024 – Aug 2025):} Delivered a 38+ service self-service Terraform module library adopted by application teams as the client's cloud-platform standard, with a tftest + PyTest suite gating every merge. Codified 1000+ preventative Config/Security-Hub controls mapped to CCMv4.0. Earned 10/10 CSAT and 3x consecutive 5/5 Pulse ratings.
    \item[$\diamond$] \textbf{DevOps Consultant – DTCC (Aug 2025 – Dec 2025):} Refactored legacy Terraform into modular, cloud-native IaC on high-sensitivity financial workloads. Used Amazon Q to accelerate code analysis and migration assessments.
    \item[$\diamond$] \textbf{MLOps Pipeline (Internal SME Program, Jun – Aug 2025):} Built the full serving stack for a SageMaker medical image classifier – TensorFlow training job, blue-green endpoint deployment, FastAPI inference API behind API Gateway + Lambda, React/CloudFront frontend, and Terraform + CodePipeline delivery with drift detection and automatic rollback.
    \item[$\diamond$] \textbf{Internal Impact:} Published APG pattern on AWS Prescriptive Guidance (\textit{Secure PR Previews and Approval-Gated Releases for Amplify Gen 2}, plus 2 more peer-reviewed in publication pipeline); 5x TFC Ambassador (AI/ML, NGDE Graduated, CloudOps, Agentic AI, Serverless); delivered 2 org-wide tech talks (Terraform testing, GitOps pipeline gating).
\resumeItemListEnd

\resumeExp
{Amazon Web Services (AWS)}{Associate Professional Services – DevOps (Internship)}{Mar 2024 – Jul 2024}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] Shipped an on-premises to AWS ECS migration with blue-green deployment via Terraform, CodePipeline, and CodeDeploy, delivering zero-downtime releases. Instrumented distributed tracing with X-Ray and CloudWatch.
\resumeItemListEnd

\resumeExp
{Ikarus-3D}{Software Developer Associate (Internship)}{May 2023 – Jul 2023}{Mohali, India}
\resumeItemListStart
    \item[$\diamond$] Containerized a production 3D-asset service on AWS ECS/ECR with a GitHub Actions CI/CD pipeline and integrated SonarQube on EC2 + RDS to enforce code-quality gates on every merge.
\resumeItemListEnd

\resumeSubHeadingListEnd
