%-----------PROJECTS-----------------
\section{\textbf{Projects}}
\vspace{-2pt}
\resumeSubHeadingListStart

\resumeExp
{\href{https://github.com/Sagargupta16/GitScope}{GitScope}}{JavaScript, Chrome Extension (Manifest V3), GitHub GraphQL API, Cloudflare Workers}{Mar 2026}{\href{https://github.com/Sagargupta16/GitScope}{\faGithub\ GitHub} | \href{https://chromewebstore.google.com/detail/gitscope/fndaanihifimmlnmkjdmjbbkbdajolff}{Chrome Web Store}}
\resumeItemListStart
    \item[$\diamond$] Chrome extension adding contribution insights to any GitHub profile -- streaks, language breakdown, PR stats, activity heatmap, and contribution charts. Published on Chrome Web Store.
    \item[$\diamond$] OAuth via Cloudflare Worker (server-side secrets), GitHub GraphQL API, 5-min caching, SPA navigation, and automatic dark/light theme adaptation. Zero runtime dependencies.
\resumeItemListEnd

\resumeExp
{\href{https://sagargupta.online/ledger-sync/}{Ledger Sync}}{TypeScript, React, FastAPI, SQLite, Tailwind CSS}{Jan 2026}{\href{https://github.com/Sagargupta16/ledger-sync}{\faGithub\ GitHub} | \href{https://sagargupta.online/ledger-sync/}{Live}}
\resumeItemListStart
    \item[$\diamond$] Self-hosted personal finance app with SHA-256 deduplication, Sankey diagrams, spending analytics, 50/30/20 budget tracking, and investment portfolio analytics across 20+ pages.
\resumeItemListEnd

\resumeExp
{\href{https://leetcode-rating-predictor.onrender.com/}{LeetCode Rating Predictor}}{Python, React, FastAPI, TensorFlow, GraphQL}{Dec 2023}{\href{https://github.com/Sagargupta16/LeetCode_Rating_Predictor}{\faGithub\ GitHub} | \href{https://leetcode-rating-predictor.onrender.com/}{Live}}
\resumeItemListStart
    \item[$\diamond$] Full-stack application with FastAPI backend, React frontend, and TensorFlow model serving. Automated data pipeline via LeetCode GraphQL API processing 244K+ records.
\resumeItemListEnd

\resumeExp
{\href{https://github.com/Sagargupta16/code-arena}{Code Arena}}{TypeScript, React, Node.js, WebSockets, Monaco Editor}{Feb 2024}{\href{https://github.com/Sagargupta16/code-arena}{\faGithub\ GitHub}}
\resumeItemListStart
    \item[$\diamond$] Real-time collaborative coding platform with WebSocket-based multiplayer, Monaco editor integration, and live code execution for competitive programming practice.
\resumeItemListEnd

\resumeSubHeadingListEnd
