%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeExp
{Amazon Web Services (AWS)}{Cloud Consultant – Professional Services (DevOps/MLOps)}{Aug 2024 – Present}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] \textbf{Lead DevOps Consultant – RWS (Feb 2026 – Present):} Own the DevOps pillar as sole consultant on RWS's data-centre-to-AWS migration, onboarding 50+ application workloads into 135+ AWS accounts. Automated multi-account provisioning with Terraform + GitHub Actions CI/CD, cutting infrastructure setup from 3+ days per account to under 4 hours (\textasciitilde90\% reduction). Designed AWS Organizations OU structure, Transit Gateway hub-and-spoke with VPN/Direct Connect hybrid connectivity, and centralized egress inspection. Enforced governance via preventative SCPs, tag policies, AWS Config rules, and Security Hub standards mapped to CCMv4. Used Kiro for AI-driven requirement analysis, architecture documentation, and implementation specs.
    \item[$\diamond$] \textbf{DevOps Consultant – State Street (Oct 2024 – Aug 2025):} Built a 38+ service self-service Terraform module library adopted by application teams as the client's cloud-platform standard, with automated unit and integration testing (tftest + PyTest) baked into every module. Architected 1000+ preventative Config/Security-Hub controls mapped to CCMv4.0 compliance. Delivered \textbf{10/10 CSAT} and \textbf{3x consecutive 5/5 Pulse} ratings.
    \item[$\diamond$] \textbf{DevOps Consultant – DTCC (Aug 2025 – Dec 2025):} Modernized legacy Terraform into cloud-native IaC patterns on high-sensitivity financial workloads – refactored monoliths into reusable modules, added remote state with S3 native locking, and hardened pipelines with policy-as-code checks. Used Amazon Q to accelerate code analysis and migration assessments across multiple workstreams.
    \item[$\diamond$] \textbf{MLOps Pipeline (Internal SME Program, Jun – Aug 2025):} Built end-to-end SageMaker pipeline for medical-image classification with blue-green endpoint deployment, auto-scaling, and drift detection – provisioned via Terraform + CodePipeline with automated rollback on canary failure.
    \item[$\diamond$] \textbf{Internal Impact:} Published APG pattern \textit{Secure PR Previews and Approval-Gated Releases for Amplify Gen 2 with GitHub} (plus 2 more peer-reviewed in the publication pipeline). Delivered 2 org-wide tech talks on Terraform module testing and GitOps pipeline gating. 5x TFC Ambassador (AI/ML, NGDE Graduated, CloudOps – AWS DevOps Agent, Agentic AI, Serverless). MLOps SME Program Graduate. Associate Speaker Certified.
\resumeItemListEnd

\resumeExp
{Amazon Web Services (AWS)}{Associate Professional Services – DevOps (Internship)}{Mar 2024 – Jul 2024}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] Migrated on-premises application to AWS ECS with blue-green deployment via Terraform, CodePipeline, and CodeDeploy – enabling zero-downtime releases. Instrumented X-Ray and CloudWatch distributed tracing for cross-service latency visibility.
\resumeItemListEnd

\resumeExp
{Ikarus-3D}{Software Developer Associate (Internship)}{May 2023 – Jul 2023}{Mohali, India}
\resumeItemListStart
    \item[$\diamond$] Containerized production application on AWS ECS/ECR with GitHub Actions CI/CD, and deployed SonarQube on EC2 + RDS to embed continuous code-quality analysis into the delivery pipeline.
\resumeItemListEnd

\resumeSubHeadingListEnd
