%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeExp
{Amazon Web Services (AWS)}{Cloud Consultant -- Professional Services (DevOps/MLOps)}{Aug 2024 -- Present}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] \textbf{Lead DevOps Consultant -- RWS (Feb 2026 -- Present):} Own the cloud-platform buildout for a data-centre migration onboarding 50+ application workloads into 135+ AWS accounts. Adopted Kiro for AI-driven requirement analysis, architecture documentation, and implementation specs, feeding those artifacts into Claude Code agent workflows and custom skills that draft Terraform modules and review PRs. Automated multi-account provisioning with Terraform + GitHub Actions, cutting infrastructure setup time by \textasciitilde90\% (3+ days per account to under 4 hours) versus manual provisioning. Designed Transit Gateway hub-and-spoke networking with VPN/Direct Connect hybrid connectivity and centralized egress inspection; enforced preventative SCPs, tag policies, AWS Config rules, and Security Hub standards aligned to CCMv4.
    \item[$\diamond$] \textbf{DevOps Consultant -- State Street (Oct 2024 -- Aug 2025):} Delivered a 38+ service self-service Terraform module library, adopted by application teams as the client's cloud-platform standard, with automated tftest + PyTest coverage on every module. Architected 1000+ preventative Config/Security-Hub controls mapped to CCMv4.0 compliance. Delivered 10/10 CSAT and 3x consecutive 5/5 Pulse ratings.
    \item[$\diamond$] \textbf{DevOps Consultant -- DTCC (Aug 2025 -- Dec 2025):} Modernized legacy Terraform to cloud-native IaC patterns on high-sensitivity financial workloads. Used Amazon Q to accelerate code analysis and migration assessments across multiple workstreams.
    \item[$\diamond$] \textbf{MLOps Pipeline (Internal SME Program, Jun -- Aug 2025):} Architected an end-to-end SageMaker MLOps pipeline for medical image classification with blue-green endpoints, auto-scaling, and drift detection. Provisioned infrastructure via Terraform + CodePipeline with CloudFront frontend and API Gateway + Lambda inference API.
    \item[$\diamond$] \textbf{Internal Impact:} Published APG pattern: Secure PR Previews and Approval-Gated Releases for Amplify Gen 2 (plus 2 more peer-reviewed in publication pipeline). 5x TFC Ambassador (AI/ML, NGDE Graduated, CloudOps, Agentic AI, Serverless). MLOps SME Program Graduate. Associate Speaker Certified; delivered 2 org-wide tech talks on Terraform testing and GitOps pipeline gating.
\resumeItemListEnd

\resumeExp
{Amazon Web Services (AWS)}{Associate Professional Services -- DevOps (Internship)}{Mar 2024 -- Jul 2024}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] Migrated on-premises application to AWS ECS with blue-green deployment via Terraform, CodePipeline, and CodeDeploy, enabling zero-downtime releases. Established observability with X-Ray and CloudWatch distributed tracing.
\resumeItemListEnd

\resumeExp
{Ikarus-3D}{Software Developer Associate (Internship)}{May 2023 -- Jul 2023}{Mohali, India}
\resumeItemListStart
    \item[$\diamond$] Containerized production application on AWS ECS/ECR with GitHub Actions CI/CD, and deployed SonarQube on EC2 + RDS to embed continuous code quality analysis into the delivery pipeline.
\resumeItemListEnd

\resumeSubHeadingListEnd
