%-----------PROJECTS-----------------
\section{\textbf{Projects}}
\vspace{-2pt}
\resumeSubHeadingListStart

\resumeExp
{\href{https://github.com/Sagargupta16/claude-skills}{Claude Skills Marketplace}}{TypeScript, Claude Code Skills, MCP Protocol, Plugin System}{2026}{\href{https://github.com/Sagargupta16/claude-skills}{\faGithub\ GitHub}}
\resumeItemListStart
    \item[$\diamond$] Public Claude Code plugin marketplace hosting 8+ skill packs (dev-workflow, CI/CD, Docker deploy, OSS contribution, deps audit, repo polish, refactoring, git advanced), each with slash commands, agents, and hooks. Skills auto-trigger on natural-language intent so users get the right tool without memorizing commands.
\resumeItemListEnd

\resumeExp
{\href{https://github.com/Sagargupta16/mcp-toolkit}{Bedrock Multi-Model MCP + MCP Toolkit}}{TypeScript, MCP Protocol, AWS Bedrock, Node.js}{2026}{\href{https://github.com/Sagargupta16/mcp-toolkit}{\faGithub\ GitHub}}
\resumeItemListStart
    \item[$\diamond$] MCP server routing a single tool call to 500+ Bedrock foundation models (Claude, Llama, Mistral, Nova, DeepSeek, Titan, Stable Diffusion, Luma). Companion toolkit standardizes MCP server config, transport, and logging across projects with a plugin architecture.
\resumeItemListEnd

\resumeExp
{\href{https://github.com/Sagargupta16/SelfHub}{SelfHub}}{TypeScript, MCP Server, MongoDB, Node.js}{Mar 2025}{\href{https://github.com/Sagargupta16/SelfHub}{\faGithub\ GitHub}}
\resumeItemListStart
    \item[$\diamond$] MCP server exposing a personal knowledge and life-ops hub (notes, tasks, journals) to Claude as structured tools. Backed by MongoDB with typed schemas so agents can read and write without hallucinating fields.
\resumeItemListEnd

\resumeExp
{\href{https://github.com/Sagargupta16/GitScope}{GitScope}}{JavaScript, Chrome Extension (Manifest V3), GitHub GraphQL, Cloudflare Workers}{Mar 2026}{\href{https://chromewebstore.google.com/detail/gitscope/fndaanihifimmlnmkjdmjbbkbdajolff}{Chrome Web Store} | \href{https://github.com/Sagargupta16/GitScope}{\faGithub\ GitHub}}
\resumeItemListStart
    \item[$\diamond$] Chrome extension published on the Chrome Web Store adding contribution insights to any GitHub profile -- streaks, language breakdown, PR stats, and activity heatmaps. OAuth via Cloudflare Worker (server-side secrets), 5-minute GraphQL response caching, zero runtime dependencies.
\resumeItemListEnd

\resumeExp
{\href{https://sagargupta.online/claude-cost-optimizer/}{Claude Cost Optimizer}}{TypeScript, Anthropic SDK, Analytics}{2026}{\href{https://sagargupta.online/claude-cost-optimizer/}{\faGlobe\ Live}}
\resumeItemListStart
    \item[$\diamond$] Tool that inspects Claude API usage and rewrites prompts, prompt-cache hits, and model routing to cut spend by 30--60\% on real workloads without changing outputs.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-1mm}
\small{\textit{Other notable projects:} LeetCode Rating Predictor (Python/FastAPI/TensorFlow, 244K+ contest records, MAE \textasciitilde14), Ledger Sync (personal-finance reconciler, TypeScript/FastAPI/SQLite), Instagram Likes Leaderboard (TypeScript/Preact).}
\vspace{-2mm}
