%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeExp
{Amazon Web Services (AWS)}{Cloud Consultant -- Professional Services (DevOps/MLOps)}{Aug 2024 -- Present}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] \textbf{Lead DevOps Consultant -- RWS (Feb 2026 -- Present):} Building RWS's cloud platform from scratch for a data-centre migration into 135+ AWS accounts (50+ application workloads), owning the full deployment lifecycle -- designed AWS Organizations OU structure, SCPs, tag policies, and Transit Gateway hub-and-spoke networking with hybrid connectivity (VPN/Direct Connect) and centralized egress inspection. Automated multi-account provisioning via Terraform + GitHub Actions CI/CD, cutting infrastructure setup time by ~90\% versus manual configuration and enabling phased workload onboarding in days instead of weeks. Enforced preventative SCPs, Config rules, and Security Hub standards -- embedding least-privilege and CCM-aligned compliance from day one. Accelerated delivery velocity by integrating Kiro for AI-driven requirement analysis and architecture specs.
    \item[$\diamond$] \textbf{DevOps Consultant -- State Street (Oct 2024 -- Aug 2025):} Achieved 10/10 CSAT and 3x consecutive 5/5 Pulse ratings delivering enterprise Terraform modules with automated unit testing (tftest, PyTest) -- enabling a 38+ service self-service platform adopted as the cloud platform standard across application teams. Architected 1000+ preventative security controls aligned with CCMv4.0 compliance, designing governance guardrails that scale with platform growth.
    \item[$\diamond$] \textbf{DevOps Consultant -- DTCC (Aug 2025 -- Dec 2025):} Modernized legacy Terraform infrastructure into secure, cloud-native IaC patterns -- unblocking DevSecOps velocity on high-sensitivity financial workloads. Leveraged Amazon Q to accelerate code analysis and migration assessments, compressing manual review cycles and enabling faster downstream infrastructure changes.
    \item[$\diamond$] \textbf{MLOps Pipeline (Internal SME Program):} Architected end-to-end SageMaker MLOps pipeline for medical image classification with blue-green endpoint deployment, auto-scaling, and drift detection -- enabling zero-downtime model updates with automatic rollback. Provisioned full infrastructure via Terraform + CodePipeline, with CloudFront frontend and API Gateway + Lambda inference API.
    \item[$\diamond$] \textbf{Internal Impact:} Published APG pattern ``Secure PR Previews \& Approval-Gated Releases for Amplify Gen 2'' (2 more peer-reviewed). MLOps SME Program Graduate. 5x TFC Ambassador (AI/ML, NGDE, CloudOps, Agentic AI, Serverless). Delivered 2 org-wide tech talks on Terraform testing and GitOps pipeline gating. Associate Speaker Certified.
\resumeItemListEnd

\resumeExp
{Amazon Web Services (AWS)}{Associate Professional Services -- DevOps (Internship)}{Mar 2024 -- Jul 2024}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] Migrated on-premises application to AWS ECS with blue-green deployment via Terraform, CodePipeline, and CodeDeploy -- enabling zero-downtime releases. Established observability with X-Ray and CloudWatch distributed tracing.
\resumeItemListEnd

\resumeExp
{Ikarus-3D}{Software Developer Associate (Internship)}{May 2023 -- Jul 2023}{Mohali, India}
\resumeItemListStart
    \item[$\diamond$] Containerized production application on AWS ECS/ECR with GitHub Actions CI/CD, and deployed SonarQube on EC2 + RDS to embed continuous code quality analysis into the delivery pipeline.
\resumeItemListEnd

\resumeSubHeadingListEnd
