%-----------PROJECTS-----------------
\section{\textbf{Personal Projects}}
\vspace{-2pt}
\resumeSubHeadingListStart

\resumeExp
{\href{https://sagargupta.online/ledger-sync/}{Ledger Sync}}{TypeScript, React 19, FastAPI, SQLite, Tailwind CSS, AWS Bedrock, OpenAI, Anthropic}{Jan 2026}{\href{https://github.com/Sagargupta16/ledger-sync}{\faGithub\ GitHub} | \href{https://sagargupta.online/ledger-sync/}{Live}}
\resumeItemListStart
    \item[$\diamond$] Self-hosted personal-finance reconciler with an AI chatbot backed by 15 read-only tool calls (App mode or BYOK, multi-provider LLM) answering spending, tax, and goal questions across 23 pages.
    \item[$\diamond$] FIRE calculator (Lean/Barista/Standard/Fat), Coast FIRE, India FY tax estimator, 8-metric Financial Health Score, Sankey cash flow, anomaly and recurring-transaction detection, SHA-256 deduplication on Excel/CSV imports.
\resumeItemListEnd

\resumeExp
{\href{https://github.com/Sagargupta16/GitScope}{GitScope}}{JavaScript, Chrome Extension (Manifest V3), GitHub GraphQL, Cloudflare Workers}{Mar 2026}{\href{https://github.com/Sagargupta16/GitScope}{\faGithub\ GitHub} | \href{https://chromewebstore.google.com/detail/gitscope/fndaanihifimmlnmkjdmjbbkbdajolff}{Chrome Web Store}}
\resumeItemListStart
    \item[$\diamond$] Published Chrome extension adding deep GitHub profile insights -- 9-stat grid, language breakdown, activity heatmap, profile comparison, follow leaderboard. OAuth handled by Cloudflare Worker (server-side secrets) with 5-minute caching and zero runtime dependencies.
\resumeItemListEnd

\resumeExp
{\href{https://sagargupta.online/claude-cost-optimizer/}{Claude Cost Optimizer}}{Claude Code Plugin, React, Vite, TypeScript, Python}{Mar 2026}{\href{https://github.com/Sagargupta16/claude-cost-optimizer}{\faGithub\ GitHub} | \href{https://sagargupta.online/claude-cost-optimizer/}{Live}}
\resumeItemListStart
    \item[$\diamond$] Installable Claude Code plugin with a cost-mode skill (lite/standard/strict) that cuts AI coding spend by 30-60\% via concise responses, model routing, and budget hooks. Ships a web Repo Analyzer (A+ to F grading), Cost Calculator, and stack-specific CLAUDE.md templates.
\resumeItemListEnd

\resumeExp
{\href{https://github.com/Sagargupta16/bedrock-multi-model-mcp}{Bedrock Multi-Model MCP}}{TypeScript, MCP Protocol, AWS Bedrock, Converse API, Nova Canvas, Nova Reel}{Apr 2026}{\href{https://github.com/Sagargupta16/bedrock-multi-model-mcp}{\faGithub\ GitHub}}
\resumeItemListStart
    \item[$\diamond$] MCP server routing through 500+ AWS Bedrock models across text (Llama 4, Mistral, Nova, Claude, Cohere, DeepSeek R1), image (Nova Canvas, SD 3.5, Titan, SDXL), and video (Nova Reel, async S3) -- with \texttt{bedrock\_ask} and \texttt{bedrock\_compare} for side-by-side evaluation across 2-5 models. Bearer-token auth fallback for enterprise use.
\resumeItemListEnd

\resumeExp
{\href{https://leetcode-rating-predictor.onrender.com/}{LeetCode Rating Predictor}}{Python, React, FastAPI, TensorFlow, GraphQL}{Dec 2023}{\href{https://github.com/Sagargupta16/LeetCode_Rating_Predictor}{\faGithub\ GitHub} | \href{https://leetcode-rating-predictor.onrender.com/}{Live}}
\resumeItemListStart
    \item[$\diamond$] Dense neural network trained on 244K+ contest records (MAE \textasciitilde14) for LeetCode rating prediction. Automated ingest via LeetCode GraphQL, 34 backend + 11 frontend tests, Docker + Render deploy.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-2pt}
\small{\textbf{Other Notable Projects:} Blue-Green AWS Terraform (18 modules, ECS Fargate + CodePipeline), Claude Skills Marketplace (25-plugin Claude Code marketplace), SelfHub (MCP personal-memory server), Instagram Likes Leaderboard (browser extension), GroundZeroNN (NN from scratch, 79.8\% MNIST).}
\vspace{-2mm}
