%-------------------------
% Resume in LaTeX
% Author : Sagar Gupta
%------------------------

\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{carlito}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}

\geometry{left=1.4cm, top=0.9cm, right=1.4cm, bottom=0.9cm}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom commands
\newcommand{\resumeExp}[4]{
\item[]
    \begin{tabular*}{\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
        \small\textbf{#1} & {\footnotesize{#3}} \vspace{-1mm} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-5mm}
}

\newcommand{\resumeEdu}[4]{
\item[]
    \begin{tabular*}{\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
        \small\textbf{#1} & \footnotesize{#3} \vspace{-1mm}\\
        \footnotesize{#2} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeAchievement}[2]{
\item[$\bullet$] \hspace{-2mm}
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
        {#1} & \textit{\footnotesize{#2}}
    \end{tabular*}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm,itemsep=0mm]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=2ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-1.5mm}}

\renewcommand{\arraystretch}{1}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}

\begin{document}

%----------HEADING-----------------
\begin{center}
    \LARGE{\textbf{Sagar Gupta}}
\end{center}
\vspace{-2mm}
\begin{center}
    \small{%
    \href{https://sagargupta.online/portfolio-react/}{\faGlobe\ sagargupta.online} \hspace{1mm}|
    \hspace{1mm} \href{https://github.com/Sagargupta16}{\faGithub\ Sagargupta16} \hspace{1mm}|
    \hspace{1mm} \href{https://www.linkedin.com/in/sagar-gupta-16-10/}{\faLinkedinSquare\ sagar-gupta-16-10} \hspace{1mm}|
    \hspace{1mm} \href{mailto:sg85207@gmail.com}{\faSend\ sg85207@gmail.com} \hspace{1mm}|
    \hspace{1mm} \faPhone\ +91-8770532413}
\end{center}
\vspace{-2mm}

%-----------SUMMARY-----------------
\section{\textbf{Summary}}
\vspace{1pt}
\small{Cloud \& DevOps/MLOps Engineer with 2 years at AWS Professional Services, delivering DevOps engagements for leading financial institutions (State Street, DTCC). Currently leading a greenfield AWS migration for 50+ workloads. Built production MLOps pipelines on SageMaker. Published AWS architecture patterns. Open source contributor to Apache Airflow, Terraform Provider AWS, and Feast. 6x AWS/Terraform certified.}
\vspace{-2mm}

%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeExp
{Amazon Web Services (AWS)}{Cloud Consultant -- Professional Services (DevOps/MLOps)}{Aug 2024 -- Present}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] \textbf{RWS -- Lead DevOps Consultant (Feb 2026 -- Present):} Leading greenfield AWS migration as the sole DevOps consultant -- designing AWS Organizations OU structure, SCPs, tag policies, and deploying Terraform infrastructure with GitHub Actions CI/CD across multi-account environments. Driving architecture decisions and defining migration roadmap for 50+ application workloads. Leveraging Kiro for AI-driven requirement analysis, architecture documentation, and implementation specs -- significantly accelerating delivery velocity.
    \item[$\diamond$] \textbf{State Street -- DevOps Consultant (Oct 2024 -- Aug 2025):} Built Terraform module library covering 38+ AWS services with automated testing (tftest, PyTest), adopted across State Street's cloud platform. Architected 1000+ preventative security controls aligned with CCMv4.0 compliance. Achieved \textbf{10/10 CSAT} and \textbf{3x consecutive 5/5 Pulse} ratings from customer.
    \item[$\diamond$] \textbf{DTCC -- DevOps Consultant (Aug 2025 -- Dec 2025):} Refactored critical Terraform infrastructure for a global financial market infrastructure firm, modernizing legacy patterns to cloud-native IaC. Leveraged Amazon Q to accelerate code analysis and migration assessments, reducing migration effort across multiple workstreams.
    \item[$\diamond$] \textbf{MLOps Pipeline (Internal SME Program):} Architected end-to-end SageMaker MLOps pipeline with blue-green deployment, auto-scaling, and drift detection for medical image classification. Provisioned full infrastructure via Terraform + CodePipeline with CloudFront frontend and API Gateway + Lambda inference API.
    \item[$\diamond$] \textbf{Internal Impact:} Published APG Pattern on AWS Prescriptive Guidance. MLOps SME Program Graduate. 4x TFC Ambassador (AI/ML, NGDE, CloudOps, Agentic AI). Delivered 2 org-wide tech talks on Terraform testing and GitOps pipeline gating. Associate Speaker Certified.
\resumeItemListEnd

\resumeExp
{Amazon Web Services (AWS)}{Associate Professional Services -- DevOps (Internship)}{Mar 2024 -- Jul 2024}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] Migrated on-premises application to AWS ECS with blue-green deployment via Terraform, CodePipeline, and CodeDeploy. Established observability with X-Ray and CloudWatch distributed tracing.
\resumeItemListEnd

\resumeExp
{Ikarus-3D}{Software Developer Associate (Internship)}{May 2023 -- Jul 2023}{Mohali, India}
\resumeItemListStart
    \item[$\diamond$] Containerized production application on AWS ECS/ECR with CI/CD via GitHub Actions and deployed SonarQube for continuous code quality analysis.
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{\textbf{Industry Certifications (6)}}
\vspace{-2pt}
\resumeItemListStart
    \resumeAchievement{\href{https://www.credly.com/badges/591e74ef-f6a8-4b77-82dc-07e06fb8060e}{AWS Certified Solutions Architect -- Associate}}{\href{https://www.credly.com/badges/591e74ef-f6a8-4b77-82dc-07e06fb8060e}{Verify}}
    \resumeAchievement{\href{https://www.credly.com/badges/be7f9e0a-593a-4544-8dfd-f69f669ec57d}{AWS Certified Developer -- Associate}}{\href{https://www.credly.com/badges/be7f9e0a-593a-4544-8dfd-f69f669ec57d}{Verify}}
    \resumeAchievement{\href{https://www.credly.com/badges/d6dc337a-0af5-48f8-b64f-eb2a5925f07b}{AWS Certified Machine Learning Engineer -- Associate}}{\href{https://www.credly.com/badges/d6dc337a-0af5-48f8-b64f-eb2a5925f07b}{Verify}}
    \resumeAchievement{\href{https://www.credly.com/badges/e18d2154-e153-40b3-8f39-6684e561396e}{AWS Certified AI Practitioner}}{\href{https://www.credly.com/badges/e18d2154-e153-40b3-8f39-6684e561396e}{Verify}}
    \resumeAchievement{\href{https://www.credly.com/badges/bf8ffb47-284c-4c45-adb8-3df4f807e404}{AWS Certified Cloud Practitioner}}{\href{https://www.credly.com/badges/bf8ffb47-284c-4c45-adb8-3df4f807e404}{Verify}}
    \resumeAchievement{\href{https://www.credly.com/badges/8b0723a5-bac7-4262-b5b6-20337b2979a1}{HashiCorp Certified: Terraform Associate (003)}}{\href{https://www.credly.com/badges/8b0723a5-bac7-4262-b5b6-20337b2979a1}{Verify}}
\resumeItemListEnd

%-----------OPEN SOURCE-----------------
\section{\textbf{Open Source Contributions}}
\vspace{-2pt}
\resumeItemListStart
    \resumeAchievement{\href{https://github.com/apache/airflow/pull/63109}{\textbf{Apache Airflow} (44K\faStarO)} -- Add template\_fields to SalesforceBulkOperator (\#63109, merged)}{}
    \resumeAchievement{\href{https://github.com/hashicorp/terraform-provider-aws/pull/46867}{\textbf{hashicorp/terraform-provider-aws} (10K\faStarO)} -- Fix IoT cloudwatch\_metric substitution template validation (\#46867)}{}
    \resumeAchievement{\href{https://github.com/feast-dev/feast/pull/6081}{\textbf{feast-dev/feast} (9K\faStarO)} -- Add Claude Code agent skills for Feast (\#6081, merged)}{}
    \resumeAchievement{\href{https://github.com/PrefectHQ/prefect/pull/20956}{\textbf{PrefectHQ/prefect} (21K\faStarO)} -- Document custom deployment steps as Python functions (\#20956, merged)}{}
    \resumeAchievement{\href{https://github.com/awslabs/mcp/pull/2607}{\textbf{awslabs/mcp} (8K\faStarO)} -- Fix Kendra documentation menu to match source directory (\#2607, merged)}{}
    \resumeAchievement{\href{https://github.com/cloudposse/terraform-aws-tfstate-backend/pull/197}{\textbf{cloudposse/terraform-aws-tfstate-backend} (437\faStarO)} -- Add S3 native locking docs, fix variable descriptions (\#197, merged)}{}
\resumeItemListEnd

%============================================================
%                       PAGE 2
%============================================================

%-----------SKILLS-----------------
\section{\textbf{Technical Skills}}
\vspace{-2pt}
\begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Cloud \& Infrastructure}{: AWS (ECS, Lambda, Organizations, SCPs, CodePipeline, EventBridge, CloudWatch, API Gateway, CloudFront), Terraform, Docker, Ansible, GitHub Actions, CI/CD, Blue-Green Deployments} \\
     \textbf{MLOps \& AI/ML}{: SageMaker (Pipelines, Endpoints, Drift Detection), TensorFlow, PyTorch, Scikit-learn, RAG Pipelines, LLMOps} \\
     \textbf{AI Developer Tools}{: Claude Code (custom skills, MCP servers, hooks, agents), GitHub Copilot, Amazon Q, Kiro, MCP Protocol} \\
     \textbf{Languages}{: Python, HCL, TypeScript, JavaScript, C++, Java, SQL} \\
     \textbf{Frameworks \& Tools}{: React, Next.js, Node.js, Express, FastAPI, MongoDB, PostgreSQL}
    }}
\end{itemize}
\vspace{-2mm}

%-----------PROJECTS-----------------
\section{\textbf{Projects}}
\vspace{-2pt}
\resumeSubHeadingListStart

\resumeExp
{\href{https://github.com/Sagargupta16/GitScope}{GitScope}}{JavaScript, Chrome Extension (Manifest V3), GitHub GraphQL API, Cloudflare Workers}{Mar 2026}{\href{https://github.com/Sagargupta16/GitScope}{\faGithub\ GitHub} | \href{https://chromewebstore.google.com/detail/gitscope/fndaanihifimmlnmkjdmjbbkbdajolff}{Chrome Web Store}}
\resumeItemListStart
    \item[$\diamond$] Chrome extension adding contribution insights to any GitHub profile -- streaks, language breakdown, PR stats, activity heatmap, and contribution charts. Published on Chrome Web Store.
    \item[$\diamond$] OAuth via Cloudflare Worker (server-side secrets), GitHub GraphQL API, 5-min caching, SPA navigation, and automatic dark/light theme adaptation. Zero runtime dependencies.
\resumeItemListEnd

\resumeExp
{\href{https://github.com/Sagargupta16/Blue_Green_AWS_Terraform}{Blue-Green AWS Terraform}}{Terraform, AWS ECS Fargate, ALB, CodePipeline, HCL}{Jul 2025}{\href{https://github.com/Sagargupta16/Blue_Green_AWS_Terraform}{\faGithub\ GitHub}}
\resumeItemListStart
    \item[$\diamond$] Production-grade IaC for zero-downtime blue-green deployments on ECS Fargate with 18 Terraform modules, KMS encryption, ALB traffic shifting, and least-privilege IAM policies.
\resumeItemListEnd

\resumeExp
{\href{https://leetcode-rating-predictor.onrender.com/}{LeetCode Rating Predictor}}{Python, React, FastAPI, TensorFlow, GraphQL}{Dec 2023}{\href{https://github.com/Sagargupta16/LeetCode_Rating_Predictor}{\faGithub\ GitHub} | \href{https://leetcode-rating-predictor.onrender.com/}{Live}}
\resumeItemListStart
    \item[$\diamond$] Dense neural network trained on 244K+ contest records achieving MAE $\sim$14 for LeetCode rating predictions. Automated data pipeline via LeetCode GraphQL API with FastAPI backend.
\resumeItemListEnd

\resumeExp
{\href{https://sagargupta.online/ledger-sync/}{Ledger Sync}}{TypeScript, React, FastAPI, SQLite, Tailwind CSS}{Jan 2026}{\href{https://github.com/Sagargupta16/ledger-sync}{\faGithub\ GitHub} | \href{https://sagargupta.online/ledger-sync/}{Live}}
\resumeItemListStart
    \item[$\diamond$] Self-hosted personal finance app with SHA-256 deduplication, Sankey diagrams, spending analytics, 50/30/20 budget tracking, and investment portfolio analytics across 20+ pages.
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{\textbf{Education}}
\resumeSubHeadingListStart
\resumeEdu
{National Institute of Technology Warangal, Telangana}{Master of Computer Applications (MCA) | NIMCET AIR 208}{Aug 2021 -- Jun 2024}{CGPA: 8.38}
\resumeEdu
{Sanskar College of Professional Studies (DAVV University), Indore}{Bachelor of Computer Applications (BCA)}{Jun 2018 -- Jun 2021}{CGPA: 7.34}
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\section{\textbf{Achievements}}
\vspace{-2pt}
\resumeItemListStart
    \resumeAchievement{Rank 1289 (Top 5\%) at Google Kick Start Round E '22.}{\href{https://github.com/Sagargupta16/Sagargupta16/blob/main/Certificates/Google-KickStart-September-2022.pdf}{Certificate}}
    \resumeAchievement{LeetCode Knight badge -- 2007 peak rating, 1200+ problems solved, 100+ contests.}{}
    \resumeAchievement{1st Place -- Coding Cauldron Online, Version '23 (NIT Trichy). 4th Place -- TriNIT Hackathon (NIT Warangal).}{}
\resumeItemListEnd

\end{document}
