%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeExp
{Amazon Web Services (AWS)}{Cloud Consultant – Professional Services (DevOps/MLOps)}{Aug 2024 – Present}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] \textbf{Lead DevOps Consultant – RWS (Feb 2026 – Present):} Sole DevOps consultant onboarding 50+ application workloads into 135+ AWS accounts, cutting infrastructure setup from 3+ days per account to under 4 hours (\textasciitilde 90\%) via Terraform + GitHub Actions provisioning pipelines. Designed AWS Organizations OU hierarchy, SCPs, tag policies, and Transit Gateway hub-and-spoke with VPN/Direct Connect hybrid connectivity and centralized egress inspection. Enforced preventative SCPs, AWS Config rules, and Security Hub standards aligned to CCMv4. Integrated Kiro for requirement analysis, architecture documentation, and implementation specs.
    \item[$\diamond$] \textbf{DevOps Consultant – State Street (Oct 2024 – Aug 2025):} Shipped a 38+ service self-service Terraform module library adopted by application teams as the client's cloud-platform standard, with automated unit testing (tftest + PyTest) gating every module. Architected 1000+ preventative Config/Security-Hub controls mapped to CCMv4.0 compliance. Delivered 10/10 CSAT, 3x consecutive 5/5 Pulse ratings.
    \item[$\diamond$] \textbf{DevOps Consultant – DTCC (Aug 2025 – Dec 2025):} Modernized legacy Terraform to cloud-native IaC patterns on high-sensitivity financial workloads. Used Amazon Q to accelerate code analysis and migration assessments.
    \item[$\diamond$] \textbf{MLOps Pipeline (SME Program, Jun – Aug 2025):} Built end-to-end SageMaker medical image classification pipeline with blue-green endpoint deployment, auto-scaling, and drift detection – zero-downtime model updates with automatic rollback. Provisioned via Terraform + CodePipeline; CloudFront frontend + API Gateway + Lambda inference.
\resumeItemListEnd

\resumeExp
{Amazon Web Services (AWS)}{Associate Professional Services – DevOps (Internship)}{Mar 2024 – Jul 2024}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] Migrated on-premises application to AWS ECS with blue-green deployment via Terraform, CodePipeline, and CodeDeploy for zero-downtime releases. Established distributed tracing with X-Ray and CloudWatch.
\resumeItemListEnd

\resumeExp
{Ikarus-3D}{Software Developer Associate (Internship)}{May 2023 – Jul 2023}{Mohali, India}
\resumeItemListStart
    \item[$\diamond$] Containerized production application on AWS ECS/ECR with GitHub Actions CI/CD; deployed SonarQube on EC2 + RDS to embed continuous code-quality analysis into the delivery pipeline.
\resumeItemListEnd

\resumeSubHeadingListEnd
