%-----------PROJECTS-----------------
\section{\textbf{Personal Projects}}
\vspace{-2pt}
\resumeSubHeadingListStart

\resumeExp
{\href{https://github.com/Sagargupta16/bedrock-multi-model-mcp}{Bedrock Multi-Model MCP}}{TypeScript, MCP Protocol, AWS Bedrock, Converse API}{Apr 2026}{\href{https://github.com/Sagargupta16/bedrock-multi-model-mcp}{\faGithub\ GitHub}}
\resumeItemListStart
    \item[$\diamond$] MCP server exposing AWS Bedrock across text (Llama 4, Mistral, Nova, Claude, DeepSeek R1), image (Nova Canvas, SD 3.5, Titan), and video (Nova Reel, async S3) -- with \texttt{bedrock\_ask} and \texttt{bedrock\_compare} for side-by-side evaluation across 2-5 models. Bearer-token auth fallback for enterprise use.
\resumeItemListEnd

\resumeExp
{\href{https://github.com/Sagargupta16/GitScope}{GitScope}}{JavaScript, Chrome Extension (Manifest V3), GitHub GraphQL, Cloudflare Workers}{Mar 2026}{\href{https://github.com/Sagargupta16/GitScope}{\faGithub\ GitHub} | \href{https://chromewebstore.google.com/detail/gitscope/fndaanihifimmlnmkjdmjbbkbdajolff}{Chrome Web Store}}
\resumeItemListStart
    \item[$\diamond$] Published Chrome extension for deep GitHub profile insights -- stat grid, language breakdown, activity heatmap, profile comparison. OAuth via Cloudflare Worker (server-side secrets), 5-min caching, zero runtime dependencies.
\resumeItemListEnd

\resumeExp
{\href{https://sagargupta.online/ledger-sync/}{Ledger Sync}}{TypeScript, React 19, FastAPI, SQLite, multi-provider LLM}{Jan 2026}{\href{https://github.com/Sagargupta16/ledger-sync}{\faGithub\ GitHub} | \href{https://sagargupta.online/ledger-sync/}{Live}}
\resumeItemListStart
    \item[$\diamond$] Self-hosted personal-finance app with an AI chatbot using 15 read-only tool calls (multi-provider LLM, BYOK) across 23 pages -- FIRE calculators, tax estimator, Sankey cash flow, anomaly detection, SHA-256 dedup on CSV/Excel imports.
\resumeItemListEnd

\resumeExp
{\href{https://leetcode-rating-predictor.onrender.com/}{LeetCode Rating Predictor}}{Python, React, FastAPI, TensorFlow, GraphQL}{Dec 2023}{\href{https://github.com/Sagargupta16/LeetCode_Rating_Predictor}{\faGithub\ GitHub} | \href{https://leetcode-rating-predictor.onrender.com/}{Live}}
\resumeItemListStart
    \item[$\diamond$] Dense neural network trained on 121K+ contest records for rating prediction. Automated data pipeline via LeetCode GraphQL, 34 backend + 11 frontend tests, Docker + Render deploy.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-2pt}
\small{\textbf{Other Notable Projects:} Blue-Green AWS Terraform (18 modules, ECS Fargate), Claude Skills Marketplace (25-plugin Claude Code marketplace), SelfHub (MCP personal memory server), GroundZeroNN (neural network from scratch, 79.8\% MNIST).}
\vspace{-2mm}
