%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeExp
{Amazon Web Services (AWS)}{Cloud Consultant – Professional Services (DevOps/MLOps)}{Aug 2024 – Present}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] \textbf{Lead DevOps Consultant – RWS (Feb 2026 – Present):} 50+ application workloads landing into 135+ AWS accounts on a greenfield platform designed from zero – Organizations OU structure, preventative SCPs, tag policies, and Transit Gateway hub-and-spoke with VPN/Direct Connect hybrid connectivity and centralized egress inspection. Cut per-account provisioning from 3+ days manual to under 4 hours (\textasciitilde90\% faster) via Terraform + GitHub Actions, enabling phased workload onboarding in days instead of weeks. Embedded CCMv4-aligned governance with AWS Config rules and Security Hub standards from day one. Integrated Kiro for AI-driven requirement analysis, architecture documentation, and implementation specs.
    \item[$\diamond$] \textbf{DevOps Consultant – State Street (Oct 2024 – Aug 2025):} 10/10 CSAT and 3x consecutive 5/5 Pulse ratings shipping a 38+ service self-service Terraform module library, adopted by application teams as the client's cloud-platform standard. Architected 1000+ preventative Config/Security-Hub controls mapped to CCMv4.0 compliance. Automated module testing with tftest + PyTest to gate every release.
    \item[$\diamond$] \textbf{DevOps Consultant – DTCC (Aug 2025 – Dec 2025):} Modernized legacy Terraform to cloud-native IaC patterns on high-sensitivity financial workloads. Used Amazon Q to accelerate code analysis and migration assessments across multiple workstreams.
    \item[$\diamond$] \textbf{MLOps Pipeline (Internal SME Program, Jun – Aug 2025):} Provisioned end-to-end SageMaker MLOps infrastructure via Terraform + CodePipeline – blue-green endpoints with auto-scaling, CloudFront frontend, API Gateway + Lambda inference, and drift detection with automatic rollback.
    \item[$\diamond$] \textbf{Internal Impact:} Published APG pattern ``Secure PR Previews and Approval-Gated Releases for Amplify Gen 2 with GitHub'' on AWS Prescriptive Guidance (plus 2 more peer-reviewed in publication pipeline). MLOps SME Program Graduate. 5x TFC Ambassador (AI/ML, NGDE Graduated, CloudOps, Agentic AI, Serverless). 2 org-wide tech talks on Terraform testing and GitOps gating. Associate Speaker Certified.
\resumeItemListEnd

\resumeExp
{Amazon Web Services (AWS)}{Associate Professional Services – DevOps (Internship)}{Mar 2024 – Jul 2024}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] Migrated on-premises application to AWS ECS with blue-green deployment via Terraform, CodePipeline, and CodeDeploy – zero-downtime releases with X-Ray and CloudWatch distributed tracing.
\resumeItemListEnd

\resumeExp
{Ikarus-3D}{Software Developer Associate (Internship)}{May 2023 – Jul 2023}{Mohali, India}
\resumeItemListStart
    \item[$\diamond$] Containerized production application on AWS ECS/ECR with GitHub Actions CI/CD; deployed SonarQube on EC2 + RDS for continuous code quality analysis.
\resumeItemListEnd

\resumeSubHeadingListEnd
