%-------------------------
% Cover Letter -- DevOps / Cloud Consultant (reusable base)
% Author : Sagar Gupta
% Usage  : Fill the 4 bracketed placeholders (COMPANY_NAME, ROLE_TITLE,
%          CITY/STATE, WHAT_EXCITES_YOU). Everything else is real and ready.
%------------------------

\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[sfdefault]{carlito}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}

\geometry{left=2.5cm, top=2.5cm, right=2.5cm, bottom=2.5cm}

\pagestyle{empty}

\begin{document}

%----------HEADER-----------------
\noindent
\textbf{\Large Sagar Gupta} \\[2pt]
\small{%
\href{mailto:sg85207@gmail.com}{\faSend\ sg85207@gmail.com} \hspace{2mm}
\href{https://www.linkedin.com/in/sagar-gupta-16-10/}{\faLinkedinSquare\ LinkedIn} \hspace{2mm}
\href{https://github.com/Sagargupta16}{\faGithub\ GitHub} \hspace{2mm}
\href{https://sagargupta.online/portfolio-react/}{\faGlobe\ Portfolio} \hspace{2mm}
\faPhone\ +91-8770532413
}

\vspace{6mm}
\noindent
\today

\vspace{4mm}
\noindent
% === FILL THESE IN ===
\textbf{Hiring Manager} \\
\textbf{COMPANY\_NAME} \\
CITY, STATE

\vspace{6mm}
\noindent
Dear Hiring Manager,

\vspace{3mm}
\noindent
% PARAGRAPH 1: Why this role + company. Replace WHAT_EXCITES_YOU with one true, specific line about them.
I am applying for the \textbf{ROLE\_TITLE} role at \textbf{COMPANY\_NAME}. I am a Cloud Consultant at AWS Professional Services with two years delivering DevOps, MLOps, and migration engagements for enterprise financial-services and technology clients, and I am drawn to COMPANY\_NAME because WHAT\_EXCITES\_YOU.

\vspace{3mm}
\noindent
% PARAGRAPH 2: Relevant experience -- all real, from INFO.md.
At AWS I currently lead a greenfield cloud migration for RWS as the sole DevOps consultant, architecting the AWS landing zone for 50+ application workloads -- Organizations OU structure, SCPs, Transit Gateway hub-and-spoke networking, and Terraform plus GitHub Actions CI/CD across multiple accounts. Earlier, I built a Terraform module library spanning 38+ AWS services with automated tftest and PyTest coverage that was adopted as the client's cloud platform standard, and I architected 1000+ preventative security controls aligned with CCMv4.0 compliance, earning a 10/10 CSAT and three consecutive 5/5 ratings.

\vspace{3mm}
\noindent
% PARAGRAPH 3: Technical depth + differentiator -- all real.
I hold six industry certifications, including AWS Solutions Architect, Developer, and Machine Learning Engineer at the Associate level plus HashiCorp Terraform Associate. Beyond client delivery, I built an end-to-end SageMaker MLOps pipeline with blue-green deployment and drift detection, published an AWS Prescriptive Guidance pattern, and serve as a 4x AWS Technical Field Community Ambassador. I contribute to open source -- merged work in Apache Airflow and Feast, with open pull requests to the Terraform AWS Provider and the Model Context Protocol SDK -- and I am a LeetCode Knight with 1200+ problems solved.

\vspace{3mm}
\noindent
% PARAGRAPH 4: Close.
I would welcome the chance to discuss how my experience building secure, automated cloud infrastructure can contribute to COMPANY\_NAME's engineering goals. Thank you for your consideration.

\vspace{6mm}
\noindent
Sincerely, \\
Sagar Gupta

\end{document}
