%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeExp
{Amazon Web Services (AWS)}{Cloud Consultant -- Professional Services (DevOps/MLOps)}{Aug 2024 -- Present}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] \textbf{MLOps Pipeline -- SME Program Graduate (Jun 2025 -- Aug 2025):} Architected end-to-end SageMaker Pipelines platform for medical image classification -- training, model registry, blue-green endpoint deployment with weighted traffic shifting, auto-scaling, and Model Monitor drift detection with automatic rollback on breach. Provisioned full infrastructure as code via Terraform + CodePipeline; exposed inference through API Gateway + Lambda with CloudFront frontend for low-latency predictions.
    \item[$\diamond$] \textbf{Lead DevOps Consultant -- RWS (Feb 2026 -- Present):} Sole DevOps consultant onboarding 50+ application workloads into 135+ AWS accounts -- designed AWS Organizations OU structure, Transit Gateway hub-and-spoke networking with VPN/Direct Connect hybrid connectivity, and centralized egress inspection. Terraform + GitHub Actions cuts infrastructure setup time by $\sim$90\% (3+ days per account to under 4 hours). Enforced preventative SCPs, tag policies, AWS Config rules, and Security Hub standards mapped to CCMv4-aligned compliance.
    \item[$\diamond$] \textbf{DevOps Consultant -- State Street (Oct 2024 -- Aug 2025):} Delivered a 38+ service self-service Terraform module library, adopted by application teams as the client's cloud-platform standard, with tftest + PyTest automated coverage. Architected 1000+ preventative Config/Security-Hub controls mapped to CCMv4.0 compliance -- governance guardrails that scaled with platform onboarding. Earned 10/10 CSAT and 3x consecutive 5/5 Pulse ratings.
    \item[$\diamond$] \textbf{DevOps Consultant -- DTCC (Aug 2025 -- Dec 2025):} Modernized legacy Terraform to cloud-native IaC patterns on high-sensitivity financial workloads. Used Amazon Q to accelerate code analysis and migration assessments.
    \item[$\diamond$] \textbf{Internal Impact:} Published APG pattern ``Secure PR Previews and Approval-Gated Releases for Amplify Gen 2'' (plus 2 more peer-reviewed in publication pipeline). 5x TFC Ambassador (AI/ML, NGDE Graduated, CloudOps, Agentic AI, Serverless). Delivered 2 org-wide tech talks on Terraform testing and GitOps pipeline gating. Associate Speaker Certified.
\resumeItemListEnd

\resumeExp
{Amazon Web Services (AWS)}{Associate Professional Services -- DevOps (Internship)}{Mar 2024 -- Jul 2024}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] Migrated on-premises application to AWS ECS with blue-green deployment via Terraform, CodePipeline, and CodeDeploy -- zero-downtime releases. Instrumented X-Ray and CloudWatch distributed tracing for production observability.
\resumeItemListEnd

\resumeExp
{Ikarus-3D}{Software Developer Associate (Internship)}{May 2023 -- Jul 2023}{Mohali, India}
\resumeItemListStart
    \item[$\diamond$] Containerized production application on AWS ECS/ECR with GitHub Actions CI/CD; deployed SonarQube on EC2 + RDS to embed continuous code quality gates into the delivery pipeline.
\resumeItemListEnd

\resumeSubHeadingListEnd
