%-----------PROJECTS-----------------
\section{\textbf{Projects}}
\vspace{-2pt}
\resumeSubHeadingListStart

\resumeExp
{\href{https://leetcode-rating-predictor.onrender.com/}{LeetCode Rating Predictor}}{Python, TensorFlow, FastAPI, React, GraphQL, Docker, Render}{Dec 2023}{\href{https://github.com/Sagargupta16/LeetCode_Rating_Predictor}{\faGithub\ GitHub} | \href{https://leetcode-rating-predictor.onrender.com/}{Live}}
\resumeItemListStart
    \item[$\diamond$] Trained dense neural network on \textbf{244K+ contest records} for post-contest rating prediction with \textbf{MAE $\sim$14} on held-out set. Automated feature engineering pipeline over LeetCode GraphQL API.
    \item[$\diamond$] Productionized full MLOps lifecycle: containerized FastAPI inference service, React frontend, 34 backend + 11 frontend tests, Docker + Render deployment with health checks.
\resumeItemListEnd

\resumeExp
{Bedrock Multi-Model MCP}{TypeScript, MCP Protocol, AWS Bedrock Converse API, Nova Canvas, Nova Reel}{Apr 2026}{\href{https://github.com/Sagargupta16/bedrock-multi-model-mcp}{\faGithub\ GitHub}}
\resumeItemListStart
    \item[$\diamond$] MCP server routing 500+ Bedrock foundation models across text (Llama 4, Mistral, Nova, Claude, Cohere, DeepSeek R1), image (Nova Canvas, SD 3.5, Titan), and video (Nova Reel async S3) -- with \texttt{bedrock\_compare} side-by-side inference evaluation across 2--5 models.
\resumeItemListEnd

\resumeExp
{\href{https://github.com/Sagargupta16/Blue_Green_AWS_Terraform}{Blue-Green AWS Terraform}}{Terraform, AWS ECS Fargate, ALB, CodePipeline, HCL}{Jul 2025}{\href{https://github.com/Sagargupta16/Blue_Green_AWS_Terraform}{\faGithub\ GitHub}}
\resumeItemListStart
    \item[$\diamond$] Production-grade IaC for zero-downtime blue-green deployments on ECS Fargate with 18 Terraform modules -- directly applicable to ML model serving with progressive traffic shifting and automated rollback.
\resumeItemListEnd

\resumeExp
{GroundZeroNN}{Python, NumPy}{2024}{\href{https://github.com/Sagargupta16/GroundZeroNN}{\faGithub\ GitHub}}
\resumeItemListStart
    \item[$\diamond$] Feedforward neural network built from scratch in NumPy -- forward/backward propagation, activation functions, mini-batch gradient descent. \textbf{79.8\% test accuracy on MNIST}, no ML frameworks.
\resumeItemListEnd

\resumeExp
{\href{https://sagargupta.online/ledger-sync/}{Ledger Sync}}{TypeScript, React, FastAPI, SQLite, AWS Bedrock, OpenAI, Anthropic}{Jan 2026}{\href{https://github.com/Sagargupta16/ledger-sync}{\faGithub\ GitHub} | \href{https://sagargupta.online/ledger-sync/}{Live}}
\resumeItemListStart
    \item[$\diamond$] Data-intensive personal finance app with SHA-256 deduplication pipeline, anomaly \& recurring transaction detection, and multi-provider LLM chatbot (15 read-only tool calls) over Excel/CSV imports.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-2pt}
\small{\textbf{Other Notable Projects:} StockSage (LSTM stock forecasting), SelfHub (MCP personal memory server), Claude Cost Optimizer (30--60\% AI cost reduction plugin), GitScope (Chrome extension), Instagram Autopilot (Bedrock Nova Canvas/Reel).}
\vspace{-2mm}
