%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeExp
{Amazon Web Services (AWS)}{Cloud Consultant – Professional Services (DevOps/MLOps)}{Aug 2024 – Present}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] \textbf{DevOps Consultant – State Street (Oct 2024 – Aug 2025):} Shipped a \textbf{38+ service self-service Terraform module library}, adopted by application teams as the client's cloud-platform standard – every module unit-tested with tftest + PyTest and consumable without platform-team intervention. Architected \textbf{1000+ preventative Config/Security-Hub controls} mapped to CCMv4.0 compliance, embedding least-privilege and audit guardrails into the module library itself. Achieved \textbf{10/10 CSAT and 3x consecutive 5/5 Pulse} ratings.
    \item[$\diamond$] \textbf{Lead DevOps Consultant – RWS (Feb 2026 – Present):} Cut per-account provisioning from \textbf{3+ days to under 4 hours ($\sim$90\%)} by owning the platform build for 50+ application workloads into 135+ AWS accounts – Terraform module library + GitHub Actions CI/CD, AWS Organizations OU structure, SCPs, tag policies, and Transit Gateway hub-and-spoke with hybrid connectivity (VPN/Direct Connect) and centralized egress inspection. Enforced preventative SCPs, tag policies, AWS Config rules, and Security Hub standards, aligning day-one deployments with CCMv4. Integrated Kiro for AI-driven requirement analysis, architecture documentation, and implementation specs.
    \item[$\diamond$] \textbf{DevOps Consultant – DTCC (Aug 2025 – Dec 2025):} Modernized legacy Terraform to cloud-native, module-driven IaC on high-sensitivity financial workloads – standardizing state, provider, and module patterns so downstream teams inherit the platform contract by default. Used Amazon Q to accelerate code analysis and migration assessments across the estate.
    \item[$\diamond$] \textbf{MLOps Platform (Internal SME Program):} Provisioned the platform layer for a SageMaker medical-image classification pipeline via Terraform + CodePipeline – blue-green endpoints, auto-scaling, drift detection, CloudFront frontend, API Gateway + Lambda inference – exposing MLOps as a repeatable pattern rather than a bespoke build.
    \item[$\diamond$] \textbf{Internal Impact:} Published APG pattern \textit{Secure PR Previews and Approval-Gated Releases for Amplify Gen 2 with GitHub} (2025), plus 2 more peer-reviewed in the publication pipeline. MLOps SME Program Graduate. \textbf{5x TFC Ambassador} (AI/ML, NGDE Graduated, CloudOps, Agentic AI, Serverless). 2 org-wide tech talks on Terraform testing and GitOps pipeline gating. Associate Speaker Certified.
\resumeItemListEnd

\resumeExp
{Amazon Web Services (AWS)}{Associate Professional Services – DevOps (Internship)}{Mar 2024 – Jul 2024}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] Enabled zero-downtime releases by migrating an on-premises application to AWS ECS with blue-green deployment via Terraform, CodePipeline, and CodeDeploy. Established observability with X-Ray and CloudWatch distributed tracing.
\resumeItemListEnd

\resumeExp
{Ikarus-3D}{Software Developer Associate (Internship)}{May 2023 – Jul 2023}{Mohali, India}
\resumeItemListStart
    \item[$\diamond$] Containerized a production application on AWS ECS/ECR with GitHub Actions CI/CD, and deployed SonarQube on EC2 + RDS to embed continuous code-quality analysis into the delivery pipeline.
\resumeItemListEnd

\resumeSubHeadingListEnd
