%-----------EXPERIENCE-----------------
\section{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeExp
{Amazon Web Services (AWS)}{Cloud Consultant – Professional Services (DevOps/MLOps)}{Aug 2024 – Present}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] \textbf{MLOps Pipeline -- SageMaker (SME Program, Jun-Aug 2025):} Trained and shipped medical image classification model on SageMaker with blue-green endpoint deployment, auto-scaling, and Model Monitor drift detection – zero-downtime updates with automatic rollback. Full IaC via Terraform + CodePipeline; API Gateway + Lambda inference API behind CloudFront frontend.
    \item[$\diamond$] \textbf{Lead DevOps Consultant -- RWS (Feb 2026 -- Present):} Cut infrastructure setup from 3+ days per account to under 4 hours ($\sim$90\%) building the platform for RWS's data-centre migration – 50+ application workloads into 135+ AWS accounts via Terraform + GitHub Actions. Designed AWS Organizations OU structure, SCPs, tag policies, and Transit Gateway hub-and-spoke networking with VPN/Direct Connect hybrid connectivity. Enforced preventative Config rules and Security Hub standards mapped to CCMv4-aligned compliance.
    \item[$\diamond$] \textbf{DevOps Consultant -- State Street (Oct 2024 -- Aug 2025):} Earned \textbf{10/10 CSAT} and \textbf{3x consecutive 5/5 Pulse} shipping a 38+ service self-service Terraform module library, adopted by application teams as the client's cloud-platform standard. Authored 1000+ preventative Config/Security-Hub controls mapped to CCMv4.0 with automated testing via tftest + PyTest.
    \item[$\diamond$] \textbf{DevOps Consultant -- DTCC (Aug 2025 -- Dec 2025):} Modernized legacy Terraform to cloud-native IaC patterns on high-sensitivity financial workloads. Used Amazon Q to accelerate code analysis and migration assessments.
    \item[$\diamond$] \textbf{Internal Impact:} MLOps SME Program Graduate (2025). Published APG pattern \textit{Secure PR Previews and Approval-Gated Releases for Amplify Gen 2} (plus 2 more peer-reviewed in publication pipeline). 5x TFC Ambassador (AI/ML, NGDE Graduated, CloudOps, Agentic AI, Serverless). Associate Speaker Certified.
\resumeItemListEnd

\resumeExp
{Amazon Web Services (AWS)}{Associate Professional Services -- DevOps (Internship)}{Mar 2024 -- Jul 2024}{Hyderabad, India}
\resumeItemListStart
    \item[$\diamond$] Migrated on-premises application to AWS ECS with blue-green deployment via Terraform, CodePipeline, and CodeDeploy – zero-downtime releases. Established observability with X-Ray and CloudWatch distributed tracing.
\resumeItemListEnd

\resumeExp
{Ikarus-3D}{Software Developer Associate (Internship)}{May 2023 -- Jul 2023}{Mohali, India}
\resumeItemListStart
    \item[$\diamond$] Containerized production application on AWS ECS/ECR with GitHub Actions CI/CD, and deployed SonarQube on EC2 + RDS to embed continuous code quality analysis into the delivery pipeline.
\resumeItemListEnd

\resumeSubHeadingListEnd
